---
title: "note 7 - iteraction"
author: "jenny"
date: "2020/11/4"
output: html_document
---

```{r, eval = FALSE}
library(tidyverse)
library(ggplot2)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

set.seed(1) #保证每次random的结果一样
```

## Lesson 1

```{r}
library(tidyverse)
library(rvest)
```

## Do something simple

```{r}
x_vec = rnorm(30, mean = 5, sd = 3)

(x_vec - mean(x_vec))/sd(x_vec)
```

Here is a founction to compute Z-scores...

```{r}
z_scores = function(x){
  if(!is.numeric(x)){
    stop("Input must be numeric")
  }
  if(length() < 3){
    stop("Input must have at least 3 numebers")
  }
  z = (x - mean(x))/sd(x)
  
  return(z)
}

z_scores(x_vec)
```

now try my function on something else. These should give errors.

```{r, error = TRUE}
z_scores(3)
z_scores(mtcars)
z_scores(c(TRUE, TRUE, FALSE))
```

## Multiple outputs

```{r}
mean_and_sd = function(x){
  if(!is.numeric(x)){
    stop("Input must be numeric")
  }
  if(length(x) < 3){
    stop("Input must have at least 3 numebers")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)
  
  tibble(
    mean = mean_x,
    sd = sd_x
  )
  
}
```

Check that function works

```{r}
x_vec = rnorm(100)
mean_and_sd(x_vec)
```

## Multiple inputs

```{r}
sim_data = 
  tiblle(
    x = rnorm(100,mean = 4, sd = 3)
  )

sim_data %>%
  summarize(
    mean = mean(x),
    sd = sd(x)
  )
```

```{r}
sim_mean_sd = function(sample_size, mu, sigma){
   sim_data = 
   tibble(
     x = rnorm(n = sample_size, mean = mu, sd = sigma)
   )

   sim_data %>%
     summarize(
       mean = mean(x),
       sd = sd(x)
   )
}

sim_mean_sd(100, 6, 3)
```

## Data in the website

```{r, eval = FALSE}
url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1"

dynamite_html = read_html(url)

review_titles = 
  dynamite_html %>%
  html_nodes(".a-text-bold span") %>%
  html_text()

review_stars = 
  dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-rating") %>%
  html_text() %>%
  str_extract("^\\d") %>%
  as.numeric()

review_text = 
  dynamite_html %>%
  html_nodes(".review-text-content span") %>%
  html_text() %>% 
  str_replace_all("\n", "") %>% 
  str_trim()

reviews_pages1 = tibble(
  title = review_titles,
  stars = review_stars,
  text = review_text
)
```

What about the next pages review

Let's turn that code into a function...

```{r}
url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1"

read_page_reviews = function(url){
  dynamite_html = read_html(url)

  review_titles = 
    dynamite_html %>%
    html_nodes(".a-text-bold span") %>%
    html_text()

  review_stars = 
    dynamite_html %>%
    html_nodes("#cm_cr-review_list .review-rating") %>%
    html_text() %>%
    str_extract("^\\d") %>%
    as.numeric()

  review_text = 
    dynamite_html %>%
    html_nodes(".review-text-content span") %>%
    html_text() %>% 
    str_replace_all("\n", "") %>% 
    str_trim()

  reviews = tibble(
    title = review_titles,
    stars = review_stars,
    text = review_text
  )
  
  reviews
}
```

Let me try my function.

```{r}
amazon_url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1"

read_page_reviews(amazon_url)
```

Let's read a few pages

```{r}
amazon_url_base = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber="

amazon_urls = str_c(amazon_url_base, 1 : 5)

all_reviewers = 
  bind_rows(
    read_page_reviews(amazon_urls[1]),
    read_page_reviews(amazon_urls[2])
  )
```

## Function as arguements

```{r}
my_summary = function(x, sum_func){
  
  sum_func(x)
}

x_vec = rnorm(100, 3, 7)

mean(x_vec)
median(x_vec)

my_summary(x_vec, median)
```

## List columns_lesson 2

## Lists

you can put anything in a list.

```{r}
l = list(vec_numeric = 5:8,
  vec_logical = c(TRUE,TRUE,FALSE,TRUE),
  mat = matrix(1:8, nrow = 2, ncol = 4),
  summary = summary(rnorm(100))
)
```

```{r}
l
l$vec_numeric
l[[1]]
```

## 'for' loop

creat a new list

```{r}
list_norm =
  list(
    a = rnorm(20, mean = 3, sd = 1),
    b = rnorm(20, mean = 2, sd = 5),
    c = rnorm(20, mean = 1, sd = 3),
    d = rnorm(20, mean = 5, sd = .2)
  )
```

```{r}
list_norm[[1]]
```

Pause and get my old function.

```{r}
mean_and_sd = function(x){
  if(!is.numeric(x)){
    stop("Input must be numeric")
  }
  if(length(x) < 3){
    stop("Input must have at least 3 numebers")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)
  
  tibble(
    mean = mean_x,
    sd = sd_x
  )
  
}
```

well, here is a loop

```{r}
output = vector("list", length = 4)

for (i in 1:4){
  output[i] = mean_and_sd(list_norm[[i]])
}

```

## Let's try map

```{r}
map(list_norm, mean_and_sd)
```

```{r}
output = map_df(list_norm, mean_and_sd, .id = "input")
```

```{r}
listcol_df = 
  tibble(
    name = c("a","b","c","d"),
    samp = list_norm
  )
```

```{r}
listcol_df %>% pull(name)
listcol_df %>%
  filter(name == "a")
```

```{r}
mean_and_sd(listcol_df$samp[[1]])
```

Can I just map?...

```{r}
map_df(listcol_df$samp, mean_and_sd, .id = "input")
```

Can I add a list column??
加一列总结在后面

```{r}
listcol_df %>%
  mutate(summary = map(samp, mean_and_sd))
```

## Weather data

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

Let's get our list columns...

firstly, put them into nested...

```{r}
weather_nest =
  weather_df %>%
  nest(data = date:tmin)
```

```{r}
weather_nest %>% pull(name)
weather_nest %>% pull(data)

weather_nest$data[[1]]
```

suppose I want to regress 'tamx' and 'tmin' for each station.

```{r}
lm(tmax ~ tmin, data = weather_nest$data[[1]])
```

```{r}
weather_lm = function(df) {
  lm(tmax ~ tmin, data = df)
}

weather_lm(weather_nest$data[[1]])
```

```{r}
weather_lm = function(df) {
  lm(tmax ~ tmin, data = df)
}

output = vector("list", 3)

for (i in 1:3){
  output[[i]] = weather_lm(weather_nest$data[[i]])
}


```

What about a map?...

```{r}
map(weather_nest$data, weather_lm)
```

What about a map in a list column??

```{r}
weather_nest =
weather_nest %>%
  mutate(models = map(data, weather_lm))
```

## lesson 3

## Let's simulate something

```{r}
sim_mean_sd = function(n, mu = 2, sigma = 3) {
  
  sim_data = tibble(
    x = rnorm(n, mean = mu, sd = sigma),
  )
  
  sim_data %>% 
    summarize(
      mean = mean(x),
      sd = sd(x)
    )
}
```

Let's start a for loop...

```{r}
output = vector("list", 100)

for (i in 1:100) {
  output[[i]] = sim_mean_sd(30)
}

bind_rows(output)
```

Let's have a new loop function.

```{r}
sim_results = 
  rerun(100, sim_mean_sd(30, 2, 3)) %>% 
  bind_rows()
```

## Let's try other sample sizes.

```{r}
n_list = 
  list(
    "n_30"  = 30, 
    "n_60"  = 60, 
    "n_120" = 120, 
    "n_240" = 240)

output = vector("list", length = 4)

for (i in 1:4) {
  output[[i]] = rerun(100, sim_mean_sd(n_list[[i]])) %>% 
    bind_rows
}
```

```{r, chache = }
sim_results = 
  tibble(sample_size = c(30, 60, 120, 240)) %>% 
  mutate(
    output_lists = map(.x = sample_size, ~rerun(200, sim_mean_sd(n = .x))),
    estimate_dfs = map(output_lists, bind_rows)) %>% 
  select(-output_lists) %>% 
  unnest(estimate_dfs)
```

DO some data frame things.

```{r}
sim_results %>%
  mutate(
    sample_size = str_c("n =", sample_size),
    sample_size = fct_inorder(sample_size)
  ) %>%
  ggplot(aes(x = sample_size, y = mean)) +
  geom_boxplot()
```

```{r}
sim_results %>%
  group_by(sample_size) %>%
  summarise(
    avg_samp_mean = mean(mean)
  )
```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```




