---
title: "note_data wrangling"
author: "jenny"
date: "2020/10/13"
output: html_document
---

## this is repository of Data wrangling i.

```{r setup}
library(tidyverse)
```

### Read in same data

```{r}
litters_df = read.csv("./data/FAS_litters.csv")
litters_df = janitor::clean_names(litters_df)
```

### take a look at the data

some methods as follows

```{r}
head(litters_df, 5)
#也可以用tail()
```


```{r}
skimr::skim(litters_df)
```

### functions in read_csv

```{r}
litters_df = read.csv("./data/FAS_litters.csv", skip = 8)
#skip表示跳过前面的几行，colnames=false表示给表格添加新的列名
names(litters_df)
```

check out `?read.csv()` for more information.

```{r}
litters_df = read.csv("./data/FAS_litters.csv")
litters_df = janitor::clean_names(litters_df)
```

## Data manipulation

###`select`

choose some columns not others

```{r}
select(litters_df, group, gd0_weight)
```

```{r}
select(litters_df, group, gd0_weight:gd_of_birth)
```

```{r}
select(litters_df, -litter_number)
```

Renaming colunms...

```{r}
select(litters_df, GROUP = group)
#只是选出你想要的列，其他列不显示
```

```{r}
rename(litters_df, GROUP = group)
```

```{r}
select(litters_df, starts_with("gd"))
#显示以某开头的列
select(litters_df, litter_number, everything())
#选择某列及之后的所有列
relocate(litters_df, litter_number)
#将某列设置为首列

```

### `filter`

```{r}
filter(litters_df, gd0_weight >= 22)
```

```{r}
filter(litters_df, gd0_weight == 20)
```

```{r}
filter(litters_df, gd0_weight >= 20, gd_of_birth == 20)
```

```{r}
filter(litters_df, group %in% c("Con7","Mod8"))
```

`drop_na(litters_data)` will remove any row with a missing value
`drop_na(litters_data, wt_increase)` will remove rows for which wt_increase is missing.

### `mutate`

```{r}
mutate(
  litters_df, 
  wt_gain = gd18_weight - gd0_weight,
  group = str_to_lower(group)
  )
#str_to_lower表示将字符变成小写
```

### `arrange`

```{r}
arrange(litters_df, pups_born_alive)
#按字母顺序排序
```

## %>%

```{r}
litters_data_raw = read.csv("./data/FAS_litters.csv")
litters_clean_name = janitor::clean_names(litters_data_raw)
litters_data_selected = select(litters_clean_name, -pups_survive)
litters_mutated = mutate(litters_data_selected, wt_gain = gd18_weight - gd0_weight)
litters_without_missing = drop_na(litters_mutated, gd0_weight)
```

Use the pipe instead.

```{r}
litters_df = (
  read.csv("./data/FAS_litters.csv") %>%
  janitor::clean_names() %>%
  select(-pups_survive) %>%
  mutate(wt_gain = gd18_weight - gd0_weight) %>%
  drop_na(gd0_weight)
)
```

















